B_pilot_2

### 2018-08-29 experiments/B_pilot_2/writeup/B_pilot_2.Rmd
renaming for B_pilot_2

---
title: "Experiment 1 of 4"
author: "Matt Green"
output:
  html_document:
    toc: yes
    <!--toc_float: true-->
    mathjax: default
    template: default
    <!--code_folding: show-->
    theme: default
---  
<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

>>>>

---
title: "B_pilot_2"
author: "Matt Green"
output:
  html_document:
    toc: yes
---

<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>
